Computer Vision-based System for Impaired Human Vision Compensation

### 2018-09-16 article.tex
Method section added

\section{Method}
\label{sec:method}

\newpage
\section{System}
\label{sec:system}

@@

>>>>

\section{Method}
\label{sec:method}
Following the principles of participatory design \cite{Kensing}, \cite{Carroll} we included the final users into the design process of the system. Two visually impaired persons participated in discussion and focus group meetings together with the project team to identify the key properties of the solution. During the six discussion sessions major attention was paid to:
\begin{enumerate}
\item Functionality and key features of the solution addressing real-life scenarios of visually impaired persons;
\item Technical feasibility, connecting user needs to the latest development in computer vision and assisted technologies;
\item Interface between the visually impaired person and the assisted technology;
\item Appearance, usability and potential costs of the final product. 
\end{enumerate}
Design process involved testing of the existing technological solutions (mobile phone apps) for assisting visually impaired persons {\color{red}(which ones have we tested?)}. Semi-structured tests were performed by the visually impaired participants accompanied by a researcher from a project group. Strengths and weaknesses of the existing solutions are reflected in the design of the proposed system.

\newpage
%patarciau skyreli vadint "Results" o ne "System".
\section{System}
\label{sec:system}

@@

\bibitem{Kensing} Kensing, F., Simonsen, J., and Bødker, K. MUST: A Method for Participatory Design. Hum-Comput Interact, vol. 13, no. 2, pp. 167–198, Jun. 1998.

\bibitem{Carroll} Carroll, J. M., Rosson, M. B. Participatory design in community informatics. Des. Stud., vol. 28, no. 3, pp. 243–261, May 2007.
